%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Approximation tildes, plusses, and minuses...
\usepackage{textcomp}
\newcommand{\textapprox}{\raisebox{0.5ex}{\texttildelow}}
\usepackage{graphicx}
\newcommand{\plus}{\raisebox{.4\height}{\scalebox{.6}{+}}}
\newcommand{\minus}{\raisebox{.4\height}{\scalebox{.8}{-}}}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1}{\small#2} & #3 \\
      \textit{\small#4} & \textit{\small #5} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Eric Doi} & Email : \href{mailto:eric.kosei.doi@gmail.com}{eric.kosei.doi@gmail.com}\\
  \href{https://www.linkedin.com/in/ericdoi/}{https://www.linkedin.com/in/ericdoi/} & Mobile : \plus65 8768-5351 / \plus1 (626) 502-7423 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Grab}{ - Southeast Asia's leading ride-hailing/deliveries/payments platform}{Singapore}
      {Lead Data Scientist}{Aug 2018 - Present}
      \resumeItemListStart
        \resumeItem{Map search relevance}
        {Spearheaded the optimization of our map search system in collaboration with engineering, product, and operations teams; set improvement roadmap, established performance metrics, standardized evaluation pipelines, tuned parameters in Elasticsearch and LTR models, and executed analyses and A/B tests.}
        \resumeItem{Growth-hacking prototypes}
        {Optimized video content using popularity heuristics for \textapprox{}4x lift in views; built user similarity graph using Locality-Sensitive Hashing for \textapprox{}5x increase in graph edges.}
      \resumeItemListEnd

    \resumeSubheading
      {Retention Science}{ - A SaaS startup for intelligent marketing}{Santa Monica, CA}
      {Data Scientist}{Apr 2015 - May 2018}
      \resumeItemListStart
        \resumeItem{Lead scoring}
          {Overhauled system to score customers' likelihood of purchase; used regularization, feature engineering, probability calibration, and operational logic to improve PR-AUC by 20x and secure client renewal.}
        \resumeItem{Product recommendations}
          {Wrote Spark pipelines using clickstream and transaction data to deliver tailored recommendations to 100M{\tiny+} users daily; e.g. used Bloom Filters for 10x speedup of duplicate removal.}
        \resumeItem{A/B testing service}
          {Created a Play/Spark service to accelerate testing of ML models in production.}
        \resumeItem{Subscription churn prediction}
          {Built a Random Forest classifier in H2O with AUC of 0.8 to aid prevention.}
        \resumeItem{Interim management}
          {Led team of 5 for 1y, triaging feature requests and upholding code standards.}
      \resumeItemListEnd

    \resumeSubheading
      {Opera Solutions}{ - Enterprise analytics software and consulting firm}{San Diego, CA}
      {Analytics Manager (2014) / Analytics Lead (2013) / Sr. Analytics Specialist (2011) }{Apr 2011 - Apr 2015}
      \resumeItemListStart
      	\resumeItem{Billing optimization}
      	  {Ran modeling, maintenance, and analysis for a live system (Patent 9,785,983) used by \textapprox{}30 auditors to recover \textapprox{}\$10M/year revenue by recommending missing HCPCS charge codes and quantities.}
        \resumeItem{Feedback model}
          {Introduced a second-layer model to learn user feedback and cut false positives by \textapprox{}30\%.}
        \resumeItem{Model deployment}
          {Trained, deployed, and evaluated models for 100{\tiny+} hospitals, with mean of \textapprox{}40\% precision.}
        \resumeItem{Management}
          {Led Delhi-based analytics team of 6, collaborated with software team, and presented to clients.} 
      \resumeItemListEnd

    \resumeSubheading
      {Laserfiche}{ - Pioneer in document imaging system software since 1987}{Long Beach, CA}
      {Software Engineer Intern}{Jun 2010 - Sep 2010}
      \resumeItemListStart
        \resumeItem{Mobile document scanner}
          {Ported an edge detection algorithm (Canny with Hough transform) from desktop to iPhone 3G; used heuristics to maintain speed and accuracy with 94\% less RAM and 80\% less CPU.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of California, San Diego}{}{La Jolla, CA}
{Master of Science in Computer Science;  GPA: 3.9}{Sep 2009 -- Mar 2011}
\resumeItemListStart
\resumeItem{Capstone}{\textit{Low-Rank Decomposition and Logistic Regression Methods for Link Prediction in Terrorist Networks}}
\resumeItemListEnd

\resumeSubheading
{Harvey Mudd College}{}{Claremont, CA}
{Bachelor of Science in Computer Science;  GPA: 3.5, with Distinction}{Aug 2005 -- May 2009}
\resumeItemListStart
\resumeItem{Research}{\textit{Grouping Strokes into Shapes in Hand-Drawn Diagrams}, AAAI 2010}
\resumeItem{Awards}{Harvey S. Mudd Merit Scholar; Harvey Mudd National Merit Scholar}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------OTHER--------------
\section{Other}
  \resumeSubHeadingListStart
    \resumeSubItem{Kaggle}
      {Top 10\% rank in rental listing classification competition (\href{github.com/ericdoi/kaggle-renthop-2017}{https://github.com/ericdoi/kaggle-renthop-2017}).}
    \resumeSubItem{Boy Scouts of America}
      {Eagle Scout and Senior Patrol Leader; led a troop of 40+ in camping, service, and growth.}
    \resumeSubItem{Interests}
      {Sustainable energy, Mandarin, cognitive psychology, armchair economics, rock climbing.}
  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \resumeItem{Software}{Languages (Scala, Python, C*, Bash), Tools (git, JIRA), Infra (AWS, Azure)}
    \resumeItem{Modeling}{Packages (SparkML, scikit-learn, numpy/scipy, R, H2O), Algorithms (Linear/Logistic Regression, Trees, Stacking, PCA, K-Means)}
    \resumeItem{Data}{ETL (Spark, Airflow, Parquet, Oozie), Analysis (SQL, pandas, Excel, cut/grep/awk, dplyr)}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
